This research, and this thesis, would not have been possible without the
love and sacrifice of the many wonderful people in my life.

Most importantly, I would like to thank Katrin Erk for all the advice given,
opportunities afforded, lessons taught, and countless hours spent. She pushed
me to try harder and look deeper, and encouraged me through difficult times.
I am honored to have worked with her, and proud of what we have accomplished,
and I am immensely grateful.

I would like to give pecial thanks to Ray Mooney, Sabine Schulte im Walde,
Jason Baldridge, and Gemma Boleda. Each has also acted as a mentor throughout
my graduate education, and I believe my perspectives on science, research, and
life have all been enhanced by their presence. Thank you also to
Risto Miikkulainen and Sebastian Pado, for serving on my committee, as well
as their helpful comments and insights.

Additional thanks to all my fellow graduate students for the many discussions
and shared experiences, both inside and outside the laboratory. Special thanks
to Islam Beltagy, Leif Johnson, Karl Pichotta, Nazneen Rajani,
Wesley Tansey, Jesse Thomason, and Subhashini Venugopalan.

Thanks to my parents Bill and Kelly, and my sisters Lindsey and Kacie, for
their investment, support, encouragement, and blind belief in my abilities.
Finally, thanks to Melanie whose support and sacrifice made this
thesis possible, and whose love made this thesis worthwhile.

\begin{flushright}
~\\
Stephen Roller\\
Austin, Texas\\
April 2017
\end{flushright}
